intro

### 2022-06-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
corrected typo

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement[@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
The effectiveness of ER strategies should therefore influence the respective SV.
A second, intrinsic, and less obvious goal is the avoidance of effort[@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and is associated with Need for Cognition (NFC)[@Caccioppo1982], a stable measure of the individual pursuit and enjoyment of cognitive effort[@Westbrook2013;@Strobel2020].
In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
Across two studies, we could show in previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
In our studies, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Moreover, the majority of participants stated afterwards the main reason for their choice was effort.
We assume therefore that, although individuals trade off both factors - effectiveness and effort - against each other, effort should be the more important predictor for SVs of ER strategies.
In addition, perceived utility should have an impact on SVs. 
A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for only one strategy or low SVs for all of the strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.

>>>>

We assume that people choose the strategy that has the highest value for them at the moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement[@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
The effectiveness of ER strategies should therefore influence the respective SV.
A second, intrinsic, and less obvious goal is the avoidance of effort[@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and is associated with Need for Cognition (NFC)[@Cacioppo1982], a stable measure of the individual pursuit and enjoyment of cognitive effort[@Westbrook2013;@Strobel2020].
In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
Across two studies, we could show in previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
In our studies, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Moreover, the majority of participants stated afterwards the main reason for their choice was effort.
We assume therefore that, although individuals trade off both factors - effectiveness and effort - against each other, effort should be the more important predictor for SVs of ER strategies.
In addition, perceived utility should have an impact on SVs. 
A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibility, however, would show high SVs only for one strategy or low SVs for all of the strategies.
This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 
Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.
